% -*- mode: LaTeX; TeX-PDF-mode: t; -*- # Tell emacs file type (for syntax coloring)
\input{./econtexRoot.texinput}
\documentclass[\econtexRoot/Letter]{subfiles}
\onlyinsubfile{\externaldocument{\econtexRoot/Letter}} % Get xrefs from main file; only works if main file has already been compiled

\begin{document}
\notinsubfile{\renewcommand{\econtexRoot}{.}}

% Details on future research agenda
Will’s job market paper has laid the foundation for an innovative research agenda that he is eager to advance. The first item on his agenda to uncover the sources of unemployment scarring and how they are influenced by the business cycle. One likely explanation is that income uncertainty pushes households to accept jobs at lower wages as a precautionary measure. Although the idea of uncertainty in driving precautionary mismatches between workers and firms has recently been explored in \cite{HuangQiu2022}, no paper, to the best of my knowledge, has explored the extent to which income uncertainty induces households to be scarred. Will intends to pursue this idea and has developed the unique technical aptitude to tackle it. Will notes that the dynamics in unemployment  risk beliefs documented in his second chapter can support this idea and highlight that perceptions in unemployment risk can induce precautionary self-induced scarring. Furthermore, Will's job market paper reveals the importance of temporary layoffs in preventing both a sluggish recovery and a permanent rise in income inequality following the COVID Recession. The manner in which he models layoffs, however, is purposely kept simple to maintain a concise message that scarring matters to macroeconomics. Will intends to write a new paper that would serve as an extension to his job market paper in which he micro-founds scarring following \cite{Gertler2022} to explore the extent fiscal stimulus during the COVID Recession induced firms to engage in temporary layoffs as opposed to permanent layoffs. In particular, \cite{Gertler2022} build a search and matching model to demonstrate that the \href{https://home.treasury.gov/policy-issues/coronavirus/assistance-for-small-businesses/paycheck-protection-program}{Paycheck Protection Program} increased employment largely by preventing temporary layoffs from becoming permanent. Integrating the search and matching micro foundations that underlie this finding into Will's general equilibrium framework that captures realistic micro consumption behavior would allow for a rigorous evaluation of the Paycheck Protection Program's role in enabling a swift recovery. More broadly, this would shed light on how fiscal policy contributed to the rapid rebound from the COVID Recession through its effects on temporary layoffs. Lastly, Will looks to explore how unemployment insurance (UI) can mitigate the effects of macro scarring induced from unemployment scarring. He emphasizes that our understanding of the transmission of UI can be enhanced by considering the fact, documented by his classmate Wonsik Ko (\href{https://www.dropbox.com/scl/fi/ps41vz5vu0o4u8cvu315b/JMP_draft_wonsik_ko.pdf?rlkey=1j1ysvonnn577154u7xb0829x&e=1&dl=0}{paper}), that scarring effects are attenuated when the unemployed receive more generous UI extensions, as this allows them to find jobs they are more satisfied with and can work more hours in. Expanding the framework in Will's job market paper to include job satisfaction could offer a new perspective on how UI can stabilize the long-run path of output.


\onlyinsubfile{\input{\LaTeXInputs/bibliography_blend}}

\ifthenelse{\boolean{Web}}{}{
  \onlyinsubfile{\captionsetup[figure]{list=no}}
  \onlyinsubfile{\captionsetup[table]{list=no}}
  \end{document}	\endinput
}

