\input{./econtexRoot.texinput}
% The skills I possess that are relevant to Bates White:
\documentclass[\econtexRoot/Letter]{subfiles}
\onlyinsubfile{\externaldocument{\econtexRoot/Letter}} % Get xrefs from main file; only works if main file has already been compiled
\begin{document}
Will possess two broad skill sets that would be useful at Bates White. 

The first is his experience in developing dynamic micro structural labor models. In his research, he has developed rich dynamic models of wealth, labor supply, and unemployment. In particular, he has built models where households make consumption decisions and choose how intensely to search in the face of unemployment risk. With these models, he has evaluated the effectiveness of unemployment insurance policies in dampening the `precautionary accelerator' in business cycle models that incorporate both a Keynesian `paradox of thrift' effect and search-and-matching models that can capture the `paradox of toil.'

His experience is not limited to models of the labor market. During his time as Ph.D.\ intern at the Bank of England, he collaborated with staff research economists to build a dynamic discrete choice model of housing. 

The second is his talent for extracting insights from large micro panel datasets, exemplified for example by his estimation (for his job market paper) of labor transition probabilities from the CPS (mentioned above). Will used these data to compute the probability of losing and finding a job over the most recently available 30 years of data. Labor economists will appreciate that this is not a trivial task, and that someone who can do this as easily as Will did can quickly master similar tasks. He has also utilized the New York Fed's Survey of Consumer Expectations to measure how households' expectations about their job-finding probabilities vary across various demographics such as education, income, and employment status. Finally, he has also figured out how to calibrate his HA model so that it can match the empirical Lorenz Curve for wealth as measured using the \emph{Survey of Consumer Finances}. 

\onlyinsubfile{\input{\LaTeXInputs/bibliography_blend}}

\ifthenelse{\boolean{Web}}{}{
  \onlyinsubfile{\captionsetup[figure]{list=no}}
  \onlyinsubfile{\captionsetup[table]{list=no}}
  \end{document} \endinput
}
